InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-29 paper.tex

>>>>

The \textbf{ai-image-det-resnet18} model is a community made, fine-tuned, resnet18 based, pretrained image detection model. For fine-tuning the author kgmann on Hugging Face used the AI or Not dataset. ResNet-18 is a convolutional neural network that is 18 layers deep. It got pretrained by over a million images from the ImageNet database. \cite{he2015deep}
